NFC and burnout in teachers - A replication and extension study

### 2022-07-25 Manuscript/Revision_Letter.Rmd
answered question about alpha level

This is our response (resolve inconsistency in tables).

>>>>

Thank you for identifying this lack of clarity.
The original data collection was done in the context of a thesis with different hypotheses than this study.
Therefore, the sample size calculation of the original data collection reads as follows:

> The initial study was aiming to recruit a sample of N ≥ 287 teachers as determined using the R package pwr (Champely, 2020), assuming a small to medium correlation of r = .20 between the measures of interest and targeting at a power of 1 − β = .80 at α = .01.

And the post-hoc power analysis of the current study is presented at the end of the same paragraph:

> Using the smallest standardized indirect effect from the mediation in Grass et al. (2018) in a post hoc power analysis with G*Power (Faul et al., 2007, 2009) yielded a power of 1 − β = .85 for linear multiple regression, given α = .05, N = 180, and f² = .05.

This is the alpha-level we had preregistered and have adhered to in the manuscript.

\Assignment{JZ}
\Done
